An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-27 4_method.tex
Tims corrections to 3.1 - 3.3 and Juns corrections to 3.4

Given an arbitrarily shaped polygon which represents the intersection of a plane and a 3D shape, our method generates a toolpath with varying width, i.e. a set of (mostly) connected line segments, with each node being assigned a width. 
The width along a line segment is linearly interpolated from the widths of its two nodes.

Our method starts with computing the skeleton of the input polygon by medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpath~\cite{eiamsa2003toward}. 
We make use of the union of cones to visualize the skeleton (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (Fig. 2?).
Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (Fig. 2?).

As depicted in Fig. 2?-?, starting from the medial axis, our method first identifies edges and nodes in the skeleton that are located in the central of the polygon (\cref{sec_center_classification}). The heights at these elements are then quantized in terms of beads. To ensure a smooth toolpath between regions with quantized integer heights that different more than two, we add new nodes in the skeleton and assign them interpolated integer heights (\cref{sec_central_height_adjustment}). The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain a toolpath with varying width (\cref{sec_toolpath_extraction}).
\jun{Do we use regular intervals, but get varying width?}

@@

This section explains how we can generate toolpaths with evenly distributed bead widths. In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.

@@

\begin{figure*}
\centering
\setlength{\figheight}{.15\textwidth}
\setlength{\figwidth}{.15\textwidth}
\setlength{\figwidthTwo}{.22\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
\caption{Layer outline}\label{}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
\caption{Skeleton}\label{}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
\caption{Union of cones}\label{}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
\caption{Slicing}\label{}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
\caption{Uniform paths}\label{}
\end{subfigure}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
The first row illustrates the generation of uniform paths (e) by interpreting the path as the intersection of horizontal planes and the union of cones (c) which is an alternative visualization of the skeleton (b). 
The second row depicts the major steps with both 2D and 3D visualizations for generating paths with adaptive width (i). Central elements in the skeleton are first identified (blue in f). The heights are then quantized in terms of beads (g, the integer values), and smoothed (h).
% A geometrical conceptualization of our technique.
% 3D visualization on top and the corresponding 2D visualization on bottom.
% In the UoC \subref{3d_surface_overview_uoc}
% we mark the central regions \subref{3d_surface_overview_center}
% and quantize the height in those regions \subref{3d_surface_overview_rounded}.
% We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
% and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
% Blue signifies regions marked as being central.
% The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

For ease of reference we have included a legend explaining \jun{this figure itself does not sufficiently "explain". How about indicating, highlighting etc?} the terms employed in this manuscript in \cref{legend}.
These terms will be further explained as they first appear later in the paper.

@@

The union of cones (UoC) is derived from a common skeletonization of the polygonal outline shape: the medial axis.
By assigning each node in the skeleton a height equal to its shortest distance to the outline we obtain the shape of the UoC.
Starting from the medial axis we further decompose the shape into simple fragments, so that the domain contains only quads and triangles. This decomposition allows to approximate the surface of the UoC as a 3D piecewise linear mesh.

%\subsubsection{Medial axis transform}
\paragraph{Medial axis transform}
The medial axis is a compact and intrinsic representation of shapes.
It is defined by the locations where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
The resulting skeleton consists of straight edges and parabolic edges.
An example is illustrated in \cref{shape_decomposition_mat}.
We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}:
\begin{equation}
    \text{sup}(v) = \argmin_{x\in P} |x - v|.
\end{equation}
Consequently the shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
%See \cref{MAT_explanation_circles}.
%We therefore represent the skeleton in a standard half-edge data-structure.
%See \cref{shape_decomposition_datastructure}.
%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
%This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
%The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
%See \cref{MAT_explanation}.
%``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.'' \cite{lee1982medial} 
%``Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.'' \cite{lee1982medial}
The medial axis along with the feature radius values along the skeleton form a complete shape descriptor, known as the medial axis transform (MAT).
%Feature radius and node locations will be used below to analyse the shape locally.

By vertically raising the center of an inscribed circle to a height that equals the center's feature radius, a right cone is formed by the inscribed circle as the base and the raised center as the apex. 
The union of cones forms a 3D solid volume. 
The medial axis can thus also be interpreted as the ridges of the volume defined by the union of cones.

%\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
%\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, the feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''

% \begin{figure}
% \centering
% \begin{subfigure}{0.3\columnwidth}
% \centering
% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
% \caption{Circles}
% \label{MAT_explanation_circles}
% \end{subfigure}
% \begin{subfigure}{0.3\columnwidth}
% \centering
% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
% \caption{Wave-fronts}
% \end{subfigure}
% \begin{subfigure}{0.3\columnwidth}
% \centering
% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
% \caption{Union of Cones}
% \end{subfigure}
% \caption{
% Medial axis representations.
% The medial axis can be defined in terms of the the number of support points of the inscribed circles,
% as the pinch sites in wave-fronts
% or as ridges in a volume defined by the union of cones.
% }
% \label{MAT_explanation}
% \end{figure}

@@

%\subsubsection{Skeletal trapezoidation}
\paragraph{Skeletal trapezoidation}
To construct the union of cones, starting from the medial axis we decompose the input polygon into a set of quads and triangles.
\jun{Tim, what is our initial purpose of skeletal trapezoidation, the purpose before we concept the approach by union of cones?}
We employ a shape decomposition similar to the one proposed by \citeauthor{Ding2016a}~\cite{Ding2016a}. 
The basic idea is to add edges connecting each node $v$ on the medial axis to (all of) its supports, $\text{sup}(v)$. 
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
Considering the fact that the concept of trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle~\cite{chazelle1984,fournier1984}, we call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).

@@

Besides the nodes that are connected by straight or parabolic edges, we insert nodes to discretize a parabolic edge into a polyline (see the middle of \cref{shape_decomposition_st}). 
The length of edges in the polyline is upper bounded by a prescribed constant $d^\text{discretization}$.
Additional nodes, with the same upper bound on the resulting edge length, are also added to discretize an edge that is formed by two concave outline vertices (see the vertex-vertex region in \cref{legend}). 
This allows to approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the medial axis by interpolating linearly between $R(v_0)$ and $R(v_1)$.

%We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
%See the middle of \cref{shape_decomposition_st}.
%That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
%This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
%; see \cref{mat_3d}.

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (floating) height value measured in terms of beads, referred to as the \emph{bead count}.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    b^*_v = 2 R(v) / w_\text{pref},
\label{eq:initialBeadCount}
\end{equation}
where $w_\text{pref}$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the 2-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
\jun{is it only a visualization or will it be used for slicing?}

\paragraph{Implementation}
The medial axis of a polygonal shape is a subset of the Voronoi Diagram (VD) generated from the line segments and vertices of the shape~\cite{lee1982medial}. 
The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and thus discarded.
Note that the Voronoi diagram contains, in addition to the medial axis, edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
From the Voronoi diagram we add nodes to discretize parabolic edges and edges formed by two concave outline vertices, and then connect all nodes to their supports, forming a skeletal trapezoidation. 
We then assign each node the bead count values using Eq.~\ref{eq:initialBeadCount}.
We compute the Voronoi diagram using the Boost \verb!C++! libraries~\cite{schaling2011boost}, which implements the algorithm proposed by \citeauthor{fortune1986sascg}~\cite{fortune1986sascg}. A half-edge data-structure is used to represent the Voronoi diagram (\cref{shape_decomposition_datastructure}).

@@

\jun{Since VD is not frequently used, I propose to suppress the use of VD. The full consequence needs to be checked.}

\subsection{Center classification}\label{sec_center_classification}
%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
%These central regions present themselves as upper ridges in the mountains of the UoC surface.
%This sections covers what parts of the UoC will be marked as being central.
\jun{TODO: For what purpose ... }
we mark parts of the UoC as being central.
The remaining is called peripheral.
Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes.

@@

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$, formed by two support edges ($vp_0$ and $vp_1$) of node $v$~\cite{attali1996modeling}. 
\jun{Bisector angle is defined on nodes, but later we classify edges on either of its nodes, or?}
Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ \jun{$w\to w_{pref}$ }when filled using the simple technique of uniform bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

Whether the bisection angle is larger than a threshold $\alpha_\text{max}$ is equivalent to if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$. See \cref{distance_based_angles}. This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
%This ratio can readily be applied to simple ST edges to determine whether they are significant.
For VD edges generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for VD edges with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization we perform when transforming the VD into the ST doesn't alter the extent and existence of marked central regions.
See \cref{legend}.
\jun{This paragraph is not clear to me. Is it related to Fig. 6? what is $x$ and what is $d$?}

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we quantize their heights.
More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$).
Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b_v/2$) coincides with a slicing height.
When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
We define a quantization operator to map a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
For examples in this section we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}.

We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow q(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

@@

\subsubsection{Quantization}
For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
We call these locations the \emph{transition anchor positions}.
Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.

We introduce the function $q^{-1}(n) := \argmax_d q(d) = n$, which gives the feature diameter at which $q$ jumps from $n$ to $n+1$ beads.
%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
See \cref{beading_transitioning_filtering__transition_mids}.

In order to prevent frequent oscillations in the bead count, we filter locally maximal or minimal bead count regions.
For each edge which contains a transition anchor we walk along the marked regions until we encounter another anchor.
If the other anchor is a transition in the opposite direction and the traversed distance is within some limit $d_\text{max}^\text{transition}$ we remove the transitions and set the bead counts at all nodes in the filtered region to the surrounding bead counts.
See \cref{beading_transitioning_filtering__filtered}.

\subsubsection{Smoothing}
In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e. where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
See \cref{transitions}.
The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.

A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.

>>>>

Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates a toolpath with varying width, i.e. a set of (mostly) connected line segments, with each junction being assigned a location and an extrusion width;
in between the junctions we linearly interpolate the position and extrusion width.

Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpaths~\cite{eiamsa2003toward}. 
We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).

As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
The heights at these elements are then quantized to an integer number of beads.
To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights in between (\cref{sec_central_height_adjustment}).
The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).

@@

This section explains how we can generate toolpaths with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed beads into a general framework for generating contour parallel toolpaths using an arbitrary beading distribution scheme and we show several such beading schemes.

@@

\begin{figure*}
\centering
\setlength{\figheight}{.15\textwidth}
\setlength{\figwidth}{.15\textwidth}
\setlength{\figwidthTwo}{.22\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
\caption{Layer outline}\label{overview_outline}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
\caption{Skeleton}\label{overview_skeleton}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
\caption{Union of cones}\label{overview_uoc}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
\caption{Slicing}\label{overview_uniform_sliced}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
\caption{Uniform paths}\label{overview_uniform_paths}
\end{subfigure}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
The first row illustrates the generation of uniform paths \subref{overview_uniform_paths}
by interpreting the path as the intersection between horizontal planes and the union of cones \subref{overview_uoc}, which is an alternative visualization of the skeleton \subref{overview_skeleton}. 
The second row depicts the stages with both 2D and 3D visualizations for generating paths with adaptive width \subref{3d_surface_overview_sliced}.
Central elements in the skeleton are first identified (blue in \subref{3d_surface_overview_center}).
The heights are then quantized in terms of number of beads (the integer values in \subref{3d_surface_overview_rounded}), and smoothed \subref{3d_surface_overview_smoothed}.
}
\label{3d_surface_overview}
\end{figure*}

For ease of reference we have included a legend showing the terms employed in this manuscript in \cref{legend}.
These terms will be further explained as they first appear later in this paper.

@@

The union of cones (UoC) is derived from a common skeletonization of the polygonal outline shape: the medial axis.
By assigning each node in the skeleton a height equal to its shortest distance to the outline we obtain the shape of the UoC.
Starting from the medial axis we further decompose the shape into simple fragments, so that the domain contains only quads and triangles.
This decomposition constitutes an approximation of the UoC.

%\subsubsection{Medial axis transform}
\paragraph{Medial axis transform}
The medial axis is a compact and complete representation of a shape.
It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
The resulting skeleton consists of straight edges and parabolic edges.
An example is illustrated in \cref{shape_decomposition_mat}.
We call the set of points on the outline polygon $P$ closest to a skeletal point $v$ its \emph{support}:
\begin{equation}
    \text{sup}(v) = \argmin_{x\in P} |x - v|.
\end{equation}
The shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
%See \cref{MAT_explanation_circles}.
%We therefore represent the skeleton in a standard half-edge data-structure.
%See \cref{shape_decomposition_datastructure}.
%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
%The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
%See \cref{MAT_explanation}.
The medial axis along with the feature radius values along the skeleton form a complete shape descriptor, known as the medial axis transform (MAT).
%Feature radius and node locations will be used below to analyse the shape locally.

By vertically raising the center of an inscribed circle to a height that equals the center's feature radius, a cone is formed. 
The union of all such cones forms a 3D solid volume. 
The medial axis can thus also be interpreted as ribs of the surface of the union of cones.~\cite{blum1967transformation}

@@

%\subsubsection{Skeletal trapezoidation}
\paragraph{Skeletal trapezoidation}
Starting from the medial axis we decompose the input polygon into a set of quads and triangles, so that we can perform the slicing stage on simple shapes.
We employ a shape decomposition similar to the one proposed by \citeauthor{Ding2016a}~\cite{Ding2016a}. 
The basic idea is to add edges connecting each node $v$ on the medial axis to (all of) its supports, $\text{sup}(v)$. 
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
Considering the fact that the concept of trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle~\cite{chazelle1984,fournier1984}, we call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).

@@

The ST contains all edges from the medial axis which are generated from two line segments in the outline polygons.
The interaction between an outline vertex and a line segment results in a parabolic region, which is discretized into pieces with a length up to $d^\text{discretization}$ (see the middle of \cref{shape_decomposition_st}).
Additionally medial axis edges which are generated from two outline vertices are also discretized, so that the feature radius $R$ in between two discretized nodes $v_0$ and $v_1$ can be approximated by linear interpolation between $R(v_0)$ and $R(v_1)$.
Again we connect the nodes which are introduced by the discretization to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count}.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    b^*_v = 2 R(v) / w_\text{pref},
\label{eq:initialBeadCount}
\end{equation}
where $w_\text{pref}$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

\paragraph{Implementation}
The medial axis of a polygonal shape is a subset of the Voronoi Diagram (VD) generated from the line segments and vertices of the shape~\cite{lee1982medial}. 
The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and thus discarded.
Note that the Voronoi diagram contains, in addition to the medial axis, edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
These extra edges are a subset of the edges connecting a node to its support, so we can leave them in.
From the Voronoi diagram we add nodes to discretize parabolic edges and edges formed by two concave outline vertices, and then connect all nodes to their supports, forming a skeletal trapezoidation. 
We then assign each node the bead count values using \cref{eq:initialBeadCount}.
We compute the Voronoi diagram using the Boost \verb!C++! libraries~\cite{schaling2011boost}, which implements the algorithm proposed by \citeauthor{fortune1986sascg}~\cite{fortune1986sascg}.
A half-edge data-structure is used to represent the Voronoi diagram (\cref{shape_decomposition_datastructure}).

@@

\subsection{Center classification}\label{sec_center_classification}
%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
%These central regions present themselves as upper ridges in the mountains of the UoC surface.
%In order to prevent the over- and underfill we will change the bead counts in the central regions.
%This sections covers what parts of the UoC will be marked as being central.
In order to prevent over- and underfill to occur in central
\jun{TODO: For what purpose ... }
we mark parts of the UoC as being central.
The remaining is called peripheral.
Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes.

@@

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting polygon points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}. 
Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_\text{pref}^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_\text{pref}$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
\begin{align}\label{simple_significance_measure}
| R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)
\end{align}
(see \cref{distance_based_angles}).
This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
For line-vertex regions and vertex-vertex regions only a portion of the region may be significant.
We therefore introduce nodes at the boundaries of the significant portion during the construction of the ST.
The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.

We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$.
We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ x_\text{bound}= 1  / \tan(\alpha_\text{max} / 2)$.
Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
The significant portion is given by $ x_\text{bound} = 1  / 2 \tan(\alpha_\text{max} / 2)$
These specific cases can easily be transformed into all possible cases using scaling and rotation operations.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we quantize their heights.
More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$, also denoted by $b^*$ for short).
Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b^*/2$) coincides with a slicing height.
When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
\jun{I like the information in the last few sentences. Shall we make it short here, and describe them in the slicing subsection.}
%\subsubsection{Initial bead count}\label{sec_initial_bead_count}

@@

%\subsubsection{Quantization}

\paragraph{Quantization}
We define a quantization operator to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
For examples in this section we first assign $b_\text{initial}$ (Eq.~\ref{eq:initialBeadCount}) to a marked node $v$ and then round it to the nearest integer: $q = \left\lfloor b_\text{initial} + \nicefrac12 \right\rfloor$.
Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}. Along with this quantization, an amendment to the marking filtering is performed, in order to alleviate a problem that will be handled in \cref{section_beading_conflicts}. Specifically, short unmarked edges (and their nodes) are marked as central if they lie between two nodes with the same integer bead count.
%We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
% From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
% If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\paragraph{Transition anchors}
For a marked edge which connects nodes $v_0$ and $v_1$ with $b^*_{v_0}\le n<b^*_{v_1}$, we determine \emph{transition anchors} at which the bead count transits from $n$ to $n+1$.
% figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
% We call these locations the \emph{transition anchor positions}.
% % Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
To this end, we introduce the function 
\begin{equation}
    q^{-1}(n) := \argmax_d q(d) = n,
\end{equation}
which gives the feature diameter $d$ at which $q$ the bead count transits from $n$ to $n+1$.
%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
The location of the anchor is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. by
% A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
% We can compute the location of the anchor simply as
\begin{equation}
    v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }.
\end{equation}
%for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
An illustration of the anchors is shown in \cref{beading_transitioning_filtering__transition_mids}.
